---
title: "Course Project - Reproducible Pitch"
author: "BSantos"
date: "5/29/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Reproducible Pitch

- Use the arrow keys to navigate through this presentation.  
- In this presentation, we will describe how "Meters & Inches converter App" works.

## Aplication Overview

In this application, there are two sliders.  

- **Slider 1:** User to select length in meters.  
Minimum: 0.01.  
Maximum: 100.  
  
- **Slider 2:** User to select length is inches.  
Minimum: 1.  
Maximum: 100.  

Converted value will be shown in respective field.  
Both sliders are independed, meaning, user does not have to use both liders in order for the App to work.


## How does it work?
**Example 1:**  
Converting a length from meters to inches:  
```{r, echo=TRUE}
    length_meters <- 2
    length_inc <- length_meters/0.0254
    length_inc
```
**Example 2:**  
Converting a length from meters to inches:  
```{r, echo=TRUE}
    length_inches <- 10
    length_m <- length_inches*0.0254
    length_m
```

## Where to find the App?

- The application can be found here:  
<https://b-santos.shinyapps.io/Meters_Inches_Converter>  

- The source code can be found here:
<https://github.com/BSantosT/Developing-Data-Products>  